Bringing the Power of eBPF to Open vSwitch

### 2018-10-29 paper.tex
Cite ovs-bpf project paper

Firstly, in OVS-eBPF project, we attach flow processing eBPF programs to TC.
We start with the most aggressive goal that we plan to re-implement the entire
features of OVS kernel datapath under net/openvswitch/* into eBPF code.
We work around a couple of eBPF limitations, for example, the lack of TLV
(Type-Length-Value) support leads us to redefine a binary kernel-user API using
a fixed-length array; without a dedicated way to execute a packet, we
create a dedicated device that attached a eBPF program to handle packet
execute logic for userspace to kernel packet transmission.
Currently, OVS-eBPF can satisfy most of the basic features for flow processing
and tunneling protocol support, and we are investigating more complicated
features such as connection tracking, NAT, (de)fragmentation, and ALG.

@@

There are several hook points where eBPF programs can be attached in recent
Linux kernels. XDP~\cite{xdp,xdp2} is another eBPF program hook point where
its attachment point is at the lowest level of the network stack.
XDP demonstrates high performance that closed to the line rate of the device,
since the eBPF programs attached to XDP hook point are triggered immediately
in the network device driver's packet receiving code path. For the same reason,
eBPF program in XDP can only access the packet data and a few metadata.
XDP supports accessing to eBPF maps and tail calls, but much less number of
helper functions is available compared to the TC hook point.

@@

\subsection{eBPF Configuration and Maps}
The OVS eBPF datapath consists of one ELF-formatted object file which provides
the full functionality of an OVS datapath. This object defines
a set of maps and a set of eBPF programs which implement a subset of
the datapath functionality.  To bootstrap, we load the eBPF program into
the kernel using \verb+iproute+. One of the programs is marked
within the ELF file to indicate that it should be
attached to the hook point; the other programs are only executed via tail
calls rooted in the eBPF hook point.  The ELF file also defines multiple persistent eBPF maps, which are
pinned to the BPF filesystem ~\cite{bpfpmap}
for sharing between different eBPF programs and \verb+ovs-vswitchd+.
The OVS datapath requires the following eBPF maps:
\begin{itemize}
\item Flow key. This is the internal representation of the protocol headers
    and metadata for the current packet being processed, defined in the P4~\cite{p4} language.
\item Flow Table. This is a hash table whose key is the 32-bit hash value
of the flow key, from both packet and its metadata,
and value equals an array of actions to execute upon the flow.
\item Stats Table. This is similar to the flow table, but rather than holding
an array of actions to execute for the packet, it contains packet and byte
statistics for the flow.
\item Perf Ring Buffer~\cite{ebpfperf,ebpfperf2}. The perf event map
allows an eBPF program to put user-defined data into a ring buffer which
may be read from a userspace program. \verb+ovs-vswitchd+ memory maps
this ring buffer to read packets and metadata from the eBPF program for
flow miss upcall processing.
\item Program Array. This map allows eBPF programs to tail call other eBPF
programs. When the BPF loader inserts eBPF programs into the kernel, it assigns
unique indexes for each program and stores these into the map.  At run time,
an eBPF program will tail call another program by referring to an index within
this map.
\end{itemize}

@@

To ensure invoking the deparser, the third experiment, set\_dst\_mac, involves
altering packet data, specifically to modify the destination MAC address. In
this case, the deparser writes stored metadata from actions processing back to
the packet. The performance in this experiment drops to $0.84$ Mpps. The drop
of $0.28$ Mpps from baseline is the result of the deparser writing all known
packet header metadata back to the packet, and due to extraneous memory copies
introduced by the P4-to-eBPF compiler. With a more intelligent deparser
implementation, and by using recent improvements to the eBPF
API~\cite{dpa1,dpa2}, the performance gap compared with the native kernel
implementation is expected to shrink.

>>>>

Firstly, in OVS-eBPF project~\cite{extensible_ovs}, we attach flow processing
eBPF programs to TC. We start with the most aggressive goal that we plan to
re-implement the entire features of OVS kernel datapath under net/openvswitch/*
into eBPF code. We work around a couple of eBPF limitations, for example, the
lack of TLV (Type-Length-Value) support leads us to redefine a binary
kernel-user API using a fixed-length array; without a dedicated way to execute
a packet, we create a dedicated device that attached a eBPF program to handle
packet execute logic for userspace to kernel packet transmission. Currently,
OVS-eBPF can satisfy most of the basic features for flow processing and
tunneling protocol support, and we are investigating more complicated features
such as connection tracking, NAT, (de)fragmentation, and ALG.

@@

There are several hook points where eBPF programs can be attached in recent
Linux kernels. XDP~\cite{xdp,xdp2,xdp-conext18} is another eBPF program hook point where
its attachment point is at the lowest level of the network stack.
XDP demonstrates high performance that closed to the line rate of the device,
since the eBPF programs attached to XDP hook point are triggered immediately
in the network device driver's packet receiving code path. For the same reason,
eBPF program in XDP can only access the packet data and a few metadata.
XDP supports accessing to eBPF maps and tail calls, but much less number of
helper functions is available compared to the TC hook point.

@@

\subsection{eBPF Configuration and Maps}
The OVS eBPF datapath consists of one ELF-formatted object file which provides
the full functionality of an OVS datapath. This object defines
a set of maps and a set of eBPF programs which implement a subset of
the datapath functionality.  To bootstrap, we load the eBPF program into
the kernel using \verb+iproute+. One of the programs is marked
within the ELF file to indicate that it should be
attached to the hook point; the other programs are only executed via tail
calls rooted in the eBPF hook point.  The ELF file also defines multiple persistent eBPF maps, which are
pinned to the BPF filesystem ~\cite{bpfpmap}
for sharing between different eBPF programs and \verb+ovs-vswitchd+.
The OVS datapath requires the following eBPF maps:
\begin{itemize}
\item Flow key. This is the internal representation of the protocol headers
    and metadata for the current packet being processed.
\item Flow Table. This is a hash table whose key is the 32-bit hash value
of the flow key, from both packet and its metadata,
and value equals an array of actions to execute upon the flow.
\item Stats Table. This is similar to the flow table, but rather than holding
an array of actions to execute for the packet, it contains packet and byte
statistics for the flow.
\item Perf Ring Buffer~\cite{ebpfperf,ebpfperf2}. The perf event map
allows an eBPF program to put user-defined data into a ring buffer which
may be read from a userspace program. \verb+ovs-vswitchd+ memory maps
this ring buffer to read packets and metadata from the eBPF program for
flow miss upcall processing.
\item Program Array. This map allows eBPF programs to tail call other eBPF
programs. When the BPF loader inserts eBPF programs into the kernel, it assigns
unique indexes for each program and stores these into the map.  At run time,
an eBPF program will tail call another program by referring to an index within
this map.
\end{itemize}

@@

To ensure invoking the deparser, the third experiment, set\_dst\_mac, involves
altering packet data, specifically to modify the destination MAC address. In
this case, the deparser writes stored metadata from actions processing back to
the packet. The performance in this experiment drops to $0.84$ Mpps. The drop
of $0.28$ Mpps from baseline is the result of the deparser writing all known
packet header metadata back to the packet. With a more intelligent deparser
implementation, and by using recent improvements to the eBPF
API~\cite{dpa1,dpa2}, the performance gap compared with the native kernel
implementation is expected to shrink.
